babette: BEAUti 2, BEAST2 and Tracer for R

### 2018-03-06 article.tex
Added feedback @rsetienne

\verb;babette; is free, libre and open source software available 
from the official R package archive at 
\url{http://cran.r-project.org/src/contrib/PACKAGES.html\#babette}
and is licensed under the GNU General Public License v3.0.
\verb;babette; uses the Travis CI (\url{https://travis-ci.org})
continuous integration service, which is known to significantly 
increase the number of bugs exposed (\cite{vasilescu2015}) and increases
the speed at which new features are added (\cite{vasilescu2015}).
\verb;babette; has a 100\% code coverage, which correlates with 
code quality (\cite{horgan1994,del1995correlation}). 
\verb;babette; follows Hadley Wickham's style guide (\cite{style_guide}), 
which improves software quality (\cite{fang2001}).
\verb;babette; depends on multiple packages, which are 
\verb;ape; (\cite{APE}), 
\verb;beautier; (\cite{beautier}),
\verb;beastier; (\cite{beastier}),
\verb;devtools; (\cite{devtools}),
\verb;geiger; (\cite{GEIGER}),
\verb;ggplot2; (\cite{ggplot2}),
\verb;knitr; (\cite{knitr}),
\verb;phangorn; (\cite{phangorn}),
\verb;rmarkdown; (\cite{rmarkdown}),
\verb;seqinr; (\cite{seqinr}),
\verb;stringr; (\cite{stringr}),
\verb;testit; (\cite{testit}) and 
\verb;tracerer; (\cite{tracerer}).
\verb;babette; is tested to give a clean 
error message for incorrect input, by
calling \verb;babette; one million times
with random or random sensible inputs, 
using the Peregrine high performance computer cluster. 
The scripts to do so, are supplied with \verb;babette;.

@@

\verb;babette;'s documentation is extensive. All functions are documented
in the package's internal documentation. For quick use, 
each exported function shows a minimal example. 
For easy exploration, each exported function's documentation links to related functions.
Additionally, \verb;babette; has a vignette that demonstrates extensively how
to use it. There is documentation on the GitHub to get started, 
with a dozen examples of BEAUti screenshots with equivalent \verb;babette; code.
Finally, \verb;babette; has some tutorial video's that can 
be downloaded or viewed on YouTube, \url{https://goo.gl/weKaaU}.

>>>>

\verb;babette; is free, libre and open source software available 
from the official R package archive at 
\url{http://cran.r-project.org/src/contrib/PACKAGES.html\#babette}
and is licensed under the GNU General Public License v3.0.
\verb;babette; uses the Travis CI (\url{https://travis-ci.org})
continuous integration service, which is known to significantly 
increase the number of bugs exposed (\cite{vasilescu2015}) and increases
the speed at which new features are added (\cite{vasilescu2015}).
\verb;babette; has a 100\% code coverage, which correlates with 
code quality (\cite{horgan1994,del1995correlation}). 
\verb;babette; follows Hadley Wickham's style guide (\cite{style_guide}), 
which improves software quality (\cite{fang2001}).
\verb;babette; depends on multiple packages, which are 
\verb;ape; (\cite{APE}), 
\verb;beautier; (\cite{beautier}),
\verb;beastier; (\cite{beastier}),
\verb;devtools; (\cite{devtools}),
\verb;geiger; (\cite{GEIGER}),
\verb;ggplot2; (\cite{ggplot2}),
\verb;knitr; (\cite{knitr}),
\verb;phangorn; (\cite{phangorn}),
\verb;rmarkdown; (\cite{rmarkdown}),
\verb;seqinr; (\cite{seqinr}),
\verb;stringr; (\cite{stringr}),
\verb;testit; (\cite{testit}) and 
\verb;tracerer; (\cite{tracerer}).
We tested \verb;babette; to give a clean 
error message for incorrect input, by
calling \verb;babette; one million times
with random or random sensible inputs, 
using the Peregrine high performance computer cluster. 
The scripts to do so are supplied with \verb;babette;.

@@

\verb;babette;'s documentation is extensive. All functions are documented
in the package's internal documentation. For quick use, 
each exported function shows a minimal example. 
For easy exploration, each exported function's documentation links to related functions.
Additionally, \verb;babette; has a vignette that demonstrates extensively how
to use it. There is documentation on the GitHub to get started, 
with a dozen examples of BEAUti screenshots with equivalent \verb;babette; code.
Finally, \verb;babette; has tutorial videos that can 
be downloaded or viewed on YouTube, \url{https://goo.gl/weKaaU}.
